# Glossary {.unnumbered}

```{r eval=FALSE, include=FALSE}
sort_def_list("glossary.Rmd")
```

Machine Learning (ML)
: Machine Learning \acr{yaml} \acr{RL}

collocation
: A collocation is a sequence of words or terms that co-occur more often than would be expected by chance

connotation (內含)
: A commonly understood cultural or emotional association that some word or phrase carries, in addition to its explicit or literal meaning, which is its *denotation*.

Direct speech act
: Locution, illocution coincide.

Grammatical Case
: The grammatical function of a noun or pronoun in a sentence. The form of the noun might change or affixes added to show its function in the sentence (not by using word order and preposition). e.g., *I*/*me*, *she*/*her*.

- nominative case: indicates the *subject* of the sentence, or the thing the subject is equivalent to.
- accusative case: indicated the *direct object* of a verb.
- genetive case: indicates that one noun is *being modified* by another one (e.g., possession).
- dative case: used for a *noun which receives something* (i.e, something moves toward that noun).
- locative case: use to indicate a *location*.
- instrumental case: used for a noun that is used as *a tool or means of completing an action*.

Grammaticalization
:  Words representing objects and actions (i.e. nouns and verbs) become grammatical markers. Creating new function words by deriving them from content words.

homonymy (ambiguity)
: A single linguistics form map onto several *unrelated* meanings.

illocution
: In pragmatica, the meaning underlying the utterance.

incorporation (併合)
: Incorporation is a phenomenon by which a grammatical category, such as a verb, forms a compound with its direct object (object incorporation) or adverbial modifier, while retaining its original syntactic function (sill verb). 
e.g., babysit, breastfeed, 睡覺

Indirect speech act
: Locution, illocution differ.
inflection
: Changes to the form of the word to show grammatical difference.

lemma
: The dictionary form of a set of words, for example, *run*, *runs*, *ran* and *running* are forms of the same lexeme, with run as the lemma.

locution
: In pragmatics, what is literally said.

Metaphor
: Understanding one kind of thing in terms of another. 

- Structural metaphor
- orientational metaphor
- ontological metaphor
    - e.g., entity, substance, container metaphor
    - personification: abstract concept -> physical object -> person
- metonymy (not metaphor): part for whole

neologism
: Newly coined lexical units or existing lexical units that acquire a new sense.
    
- old words with new senses
- new coinages
- derived words

nominalization (名詞化)
: The use of a word which is not a noun (e.g., a verb, an adjective or an adverb) as a noun, or as the head of a noun phrase, with or without morphological transformation.

polysemy
: A single linguistics form map onto several *related* meanings.

rhotic vowel (兒化)
: Aka *vocalic r*, *r-colored*, *retroflex*, and *rhotacized* vowel, is a vowel that is modified in a way that results in a lowering in frequency of the third formant.

Semantic role
: A semantic role is the underlying *relationship* that a *participant*(noun) has with the main *verb*.
(the role in relation to the predicate of the sentence)

Syncretism
: Syncretism exists when functionally distinct occurrences of a single lexeme, morph or phone are identical in form.
```{r echo=FALSE}
table <- data.frame("past tense" = "walked",
                    "past participle" = "walked")
knitr::kable(table, format = 'latex')
```

synonymy
: Several forms map onto (more or less) same meaning.

vagueness
: Two or more meanings associated with a given phonological form are united as non-distinguished subcases of a single, more general meaning
e.g., child.

Vowel space area (VSA)
: The two-dimensional area bounded by lines connecting *first and second formant frequency* coordinates (F1/F2) of vowels.
Since frequencies of the first and second formants roughly relate to the size and shape of the cavities created by jaw opening (F1) and tongue position (F2), the VSA is an acoustic proxy for the kinematic displacements of the articulators.

word sense
: One of the meanings of a word.